Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-14 paper/main.tex
Cython/us overhead in bindings discussion

\subsection{Small files}
For small files, 1B and 1KB, we can clearly see that both double \ac{SHA}-256 
greatly outperforms the \ac{SHA}-3 candidate implementations. The data being 
hashed for these files are dominated by lengths of 63 and 106 bytes. By 
comparing with \ac{SUPERCOP} results, and especially the fact that we are 
using double \ac{SHA}-256, which should result in large overhead this is
unexpected.

\subsection{Large files}
For large files, 1MB, 100MB and 1GB, some of the \ac{SHA}-3 candidates are 
actually outperforming double \ac{SHA}-256, which is expected from the
\ac{SUPERCOP} results. However if we compare this result with the result for
small files, and expect that a hash algorithm should do better on a cycles/byte
basis when hashing larger data values this is not expected. Data sizes which
are hashed during 1GB and 100MB up/downloads are dominated by 101B, 65569B and
131106B. 50\% of the hashes are done on 101B, which is a size which should be
largely affected by having to do double SHA-256. However, since the small files
had a similar percentage of operations being done on 106B chunks, blaming need
to use double \ac{SHA}256 is not enough. It looks like indeed the large data
chunks being hashed is what is making the difference.

>>>>

\subsection{Small files}
For small files, 1B and 1KB, we can clearly see that both double \ac{SHA}-256 
greatly outperforms the \ac{SHA}-3 candidate implementations. The data being 
hashed for these files are dominated by lengths of 63 and 106 bytes. By 
comparing with \ac{SUPERCOP} results, and especially the fact that we are 
using double \ac{SHA}-256, which should result in large overhead this is
unexpected. However, we believe that the results for small files may also
reflect our use of Cython and our skill. Given large amounts of call to our
bindings, while the data processed by the actual hash functions is small and
therefore does not use a lot of time, the speed of the bindings will come in to
play.

\subsection{Large files}
For large files, 1MB, 100MB and 1GB, some of the \ac{SHA}-3 candidates are 
actually outperforming double \ac{SHA}-256, which is expected from the
\ac{SUPERCOP} results. However if we compare this result with the result for
small files, and expect that a hash algorithm should do better on a cycles/byte
basis when hashing larger data values this is not expected. Data sizes which
are hashed during 1GB and 100MB up/downloads are dominated by 101B, 65569B and
131106B. 50\% of the hashes are done on 101B, which is a size which should be
largely affected by having to do double SHA-256. However, since the small files
had a similar percentage of operations being done on 106B chunks, blaming need
to use double \ac{SHA}256 is not enough. It looks like indeed the large data
chunks being hashed is what is making the difference. If we now consider that
our bindings to the hash functions is what is causing the slow results for
small files, this makes sense. Larger amounts of data will take longer to
process for the hash function, which again results in the fraction of time used
by our bindings is decreased.

%FIXME: Nevn noe en plass om at vi kanskje burde timet kallene til HASH
%funksjonen også.
